Differential Expression - HBCC - STG - Dx

### 2020-08-19 individual-cohorts/split_by_analysis/HBCC_DLPFC_DE_Diagnosis.Rmd
revert

```{r knit2synapse, eval=FALSE}
library(synapser)
library(knit2synapse)

@@

knit2synapse::createAndKnitToFolderEntity(file = "individual-cohorts/split_by_analysis/HBCC_DLPFC_DE_Diagnosis.Rmd",
                                 parentId ="syn22050019",
                                 folderName = "Differential Expression - Dx")
```

>>>>

```{r knit2synapse, eval=FALSE}
render::rmarkdown("individual-cohorts/split_by_analysis/HBCC_DLPFC_DE_Diagnosis.Rmd")

library(synapser)
library(knit2synapse)

@@

knit2synapse::createAndKnitToFolderEntity(file = "individual-cohorts/split_by_analysis/HBCC_DLPFC_DE_Diagnosis.Rmd",
                                 parentId ="syn22050019",
                                 folderName = "Differential Expression - Dx",
                                 knitmd=FALSE)
```

### 2020-08-19 individual-cohorts/split_by_analysis/HBCC_STG_DE_Diagnosis.Rmd
revert

# Fit linear model using new weights and new design
# VOOM.GENE_EXPRESSION$E = CQN.GENE_EXPRESSION
ADJUSTED.FIT = variancePartition::dream(exprObj = VOOM.GENE_EXPRESSION$E,
                                        formula = formula,
                                        data = COVARIATES,
                                        computeResiduals = TRUE)

>>>>

# Fit linear model using new weights and new design
VOOM.GENE_EXPRESSION$E = CQN.GENE_EXPRESSION
ADJUSTED.FIT = variancePartition::dream(exprObj = VOOM.GENE_EXPRESSION$E,
                                        formula = formula,
                                        data = COVARIATES,
                                        computeResiduals = TRUE)
